---
title: "Experiment 2 - Analysis"
author: "Bodo Winter"
date: "7/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminaries:

Load packages:

```{r}
library(tidyverse)
library(brms)
```

Load in data:

```{r}
header <- readLines('../data/E2_handshape.csv', n = 1)
E2 <- read_csv('../data/E2_handshape.csv', skip = 2,
               col_names = FALSE)
colnames(E2) <- unlist(str_split(header, ','))
```

Rename relevant columns:

```{r}
E2 <- rename(E2,
             Control = MathQuestion,
             Age = age,
             Gender = gender,
             Handedness = handedness,
             NativeLanguage = language,
             Condition = `DO-BR-FL_10`,
             Comments = OpenEnded,
             Notice = GestureNotice,
             ViewN = VideoNTimes,
             ViewYes = VideoCompletion,
             IP = V6,
             StartTime = V8,
             FinishTime = V9)
```

Get all_responses:

```{r}
# Initialize empty column for responses:

E2$Response <- NA

# The relevant columns all have '_resp':

these_cols <- str_detect(colnames(E2), 'E2_')

# The relevant columns all have '_resp':

for (i in 1:nrow(E2)) {
  this <- unlist(E2[i, these_cols])
  names(this) <- c()
  if (!all(is.na(this))) {
    E2[i, ]$Response <- this[!is.na(this)]
  }
  }
```

There's some issue with the file, let's get rid of the respective columns:

Select subset of dataframe with relevant columns:

```{r}
E2 <- select(E2,
             ViewYes:NativeLanguage, IP, Notice, Condition, StartTime, FinishTime, Response)
```

Exclude those partials that did not respond and report loss. For proper reporting (since there will be several rounds of exclusion), it makes sense to create a tibble:

```{r}
# Original tibble:

excl_tib <- tibble(N = nrow(E2), Type = 'Original')

# Those that didn't respond:

E2 <- filter(E2, !is.na(Response))

# New tibble to keep track of exclusions:

new_tib <- tibble(N = nrow(E2), Type = 'after partials')
excl_tib <- bind_rows(excl_tib, new_tib)
```

Exclude those that are duplicated responses (from the same IP):

```{r}
# Those that didn't respond:

these_IPs <- filter(E2, duplicated(IP)) %>% pull(IP)
E2 <- filter(E2, !(IP %in% these_IPs))

# New tibble to keep track of exclusions:

new_tib <- tibble(N = nrow(E2), Type = 'after duplicates')
excl_tib <- bind_rows(excl_tib, new_tib)
```

Get rid of non-native speakers:

```{r}
# Vector of things to exclude:

excludes <- c('Russian, English', 'Nepali', 'Telugu')

# Exclude:

E2 <- filter(E2, !(NativeLanguage %in% excludes))

# New tibble to keep track of exclusions:

new_tib <- tibble(N = nrow(E2), Type = 'after non-natives')
excl_tib <- bind_rows(excl_tib, new_tib)
```

Get rid of people who couldn't view the videos:

```{r}
# Exclude:

E2 <- filter(E2, ViewYes == 'Yes')

# Get rid of those that report to have had a viewing problem:

excludes <- c("Video was lagging",
              "it buffered for a few seconds while viewing then continued.. that is why I had to view twice",
              "The video buffered a couple of times so I rewatched after it had completely loaded",
              "no had a little buffer but alright",
              "It was a bit glitchy.",
              "it took a long time to load and was a little choppy",
              "Yes, it didn't play correctly the first time.",
              "The picture took two plays to load.")

# Exclude these:

exclude_ids <- which(E2$VideoIssues %in% excludes)
E2 <- E2[-exclude_ids, ]

excludes <- c("Twice because it loaded slowly.",
              "2 days")
exclude_ids <- which(E2$ViewN %in% excludes)
E2 <- E2[-exclude_ids, ]

# New tibble to keep track of exclusions:

new_tib <- tibble(N = nrow(E2), Type = 'after viewing problems')
excl_tib <- bind_rows(excl_tib, new_tib)
```

Process viewing times:

```{r}
# Make it into lowercase for easier processing:

E2 <- mutate(E2, ViewN = str_to_lower(ViewN))

# Create a table that matches responses to counts:

ViewN <- c('1', 'once', 'one', "1.5", "once.", "1 time",
           '2', 'two', 'twice', '2 times',
           'three', '3', '3 because i had a hard time understanding what he was saying because of his accent.', "3 times",
           "4", "5")
ViewCount = c(1, 1, 1, 1, 1, 1,
              2, 2, 2, 2,
              3, 3, 3, 3,
              4, 5)
key <- tibble(ViewN, ViewCount)

# Merge these counts into the data frame:

E2 <- left_join(E2, key)
```

Assess whether the viewing times depend on condition:

```{r}
E2 %>% group_by(Condition) %>% 
  summarize(sum = sum(ViewCount))
```

Not massive differences...

Create the Monday/Friday column:

```{r}
E2 <- mutate(E2, Response = str_to_lower(Response))

E2$RespClean <- NA
E2[str_detect(E2$Response, 'monday'), ]$RespClean <- 'monday'
E2[str_detect(E2$Response, 'friday'), ]$RespClean <- 'friday'

# Exclude those that responded neither monday nor friday:

E2 <- filter(E2, !is.na(RespClean))

# New tibble to keep track of exclusions:

new_tib <- tibble(N = nrow(E2), Type = 'after wrong-day responders')
excl_tib <- bind_rows(excl_tib, new_tib)
```

Code for multiple views versus single views:

```{r}
# If you wanted to take only those that had only one view:

# E2 <- filter(E2, ViewCount == 1)

# Multiple viewers as a separate variable:

E2 <- mutate(E2,
             MultipleView = ifelse(ViewCount == 1, 'single', 'multiple'))

# New tibble to keep track of exclusions (only necessary if excluded):

# new_tib <- tibble(N = nrow(E2), Type = 'after multiple viewers')
# excl_tib <- bind_rows(excl_tib, new_tib)
```

Code condition column:

```{r}
conditions <- str_split(E2$Condition, pattern = '_', simplify = TRUE)

E2$HandNumber <- conditions[, 2]
E2$HandShape <- conditions[, 3]
E2$Direction <- conditions[, 4]
```

Get rid of the original response column:

```{r}
E2 <- mutate(E2,
             Response = RespClean) %>% 
  select(-RespClean)
```

For plotting make it so that the Response factor is "monday", then "friday" (easier: from left to right).

```{r}
E2 <- mutate(E2,
             Response = str_to_title(Response),
             Response = factor(Response, levels = c('Monday', 'Friday')))
```

Change the labels in the Gesture and Language columns to make them better for plotting, and order factors for plotting:

```{r}
E2 <- mutate(E2,
             HandShape = ifelse(HandShape == 'FLAT', 'flat', 'push'),
             HandShape = factor(HandShape),
             Direction = ifelse(Direction == 'FORW', 'forward', 'backward'),
             DirectionPlot = str_c(Direction, '\ngesture'),
             Direction = factor(Direction,
                                levels = c('backward', 'forward')),
             DirectionPlot = factor(DirectionPlot, levels = c('forward\ngesture', 'backward\ngesture')),
             HandNumber = ifelse(HandNumber == 'SH', 'single-handed', 'two-handed'),
             HandNumber = factor(HandNumber))
```

Overview of exclusions:

```{r}
excl_tib$Exclusions <- c(0, abs(diff(excl_tib$N)))
excl_tib$Prop <- NA
for (i in 2:nrow(excl_tib)) {
  excl_tib[i, ]$Prop <- excl_tib[i, ]$N / excl_tib[i - 1, ]$N
}
excl_tib <- mutate(excl_tib, Prop = 1 - Prop)
excl_tib
```

And the overall exclusion:

```{r}
excl_tib[1, ]$N - excl_tib[nrow(excl_tib), ]$N
(excl_tib[1, ]$N - excl_tib[nrow(excl_tib), ]$N) / excl_tib[1, ]$N
```


What's reported in the paper is the following, the number of participants that are actually participants of the study (N = 239) compared to the 191 participants that are included in the analysis.

```{r}
orig <- filter(excl_tib, Type == 'after duplicates')$N
final <- filter(excl_tib, Type == 'after wrong-day responders')$N
orig - final
1 - (final / orig)
```

Check the comprehension question:

```{r}
all(E1$Control == 13)
```

What does the total sample consist of in terms of demographics?

```{r}
table(E2$Gender)
mean(as.numeric(E2$Age), na.rm = TRUE)
range(as.numeric(E2$Age), na.rm = TRUE)
```


## Descriptive stats and visualizations:

First, how many were aware of the gestures?

```{r}
E2 %>% count(Notice, sort = TRUE)
```

Lots of them.

Tabulations of the main result:

```{r}
E2 %>% count(Response)
round(prop.table(table(E2$Response)), 2)
```

Overall many more Monday responses.

```{r}
with(E2, table(Direction, Response))
round(prop.table(with(E2, table(Direction, Response)), 1), 2)
```

HandShape effect:

```{r}
with(E2, table(HandShape, Response))
round(prop.table(with(E2, table(HandShape, Response)), 1), 2)
```

Hand number / direction effect:

```{r}
xtab <- with(E2, table(Direction, Response, HandNumber))
single <- xtab[, , 1]
two <- xtab[, , 2]
single
two
prop.table(single, 1)
prop.table(single, 2)

```

More Monday responses when the language is backwards.

```{r}
E2 %>% count(HandNumber, Direction, Response)
```

Handshape:

```{r}
E2 %>% count(HandShape, Direction, Response)
```

Looks to be some stuff.

```{r, fig.width = 10, fig.height = 6}
E2 %>%
  count(Direction, HandShape, Response) %>%
  ggplot(aes(x = HandShape, y = n, fill = Response)) +
  geom_bar(stat = 'identity', col = 'black',
           position = 'dodge') + 
  scale_fill_viridis_d(option = 'D', direction = -1) +
  theme_minimal() +
  ylim(0, 50) +
  theme(legend.position = 'top') +
  facet_wrap(~Direction)
```

## Publication ready stacked bar plot:

Stacked bar plot with percentages:

```{r, fig.width = 9, fig.height = 5}
E2 %>%
  count(HandShape, DirectionPlot, Response) %>%
  spread(Response, n) %>%
  mutate(Sum = Monday + Friday,
         Monday = Monday / Sum,
         Friday = Friday / Sum) %>%
  select(-Sum) %>%
  gather(key = 'Response', value = 'n',
         -(HandShape:DirectionPlot)) %>%
  mutate(Response = factor(Response,
                           levels = c('Monday', 'Friday'))) %>%
  rename(Proportion = n) %>% 
  ggplot(aes(x = DirectionPlot, y = Proportion, fill = Response)) +
  geom_bar(stat = 'identity', col = 'black',
           position = position_stack(reverse = TRUE),
           width = 0.5) + 
  scale_fill_manual(values = c('#FDE725FF', '#21908CFF')) +
  theme_minimal() +
  theme(legend.position = 'right') +
  facet_wrap(~HandShape) +
  labs(title = 'Monday/Friday responses by\nHand Shape and Gesture Direction',
       caption = str_c('N = ', nrow(E2), ', Amazon Mechanical Turk')) +
  ylab('Proportion\n') +
  xlab('') +
  theme(plot.title = element_text(face = 'bold', size = 20, hjust = 0.5),
        axis.title = element_text(face = 'bold', size = 24),
        axis.text.x = element_text(face = 'bold', size = 20),
        axis.text.y = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 20),
        plot.caption = element_text(size = 14),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())
ggsave('../figures/experiment2_hand_shape.png', width = 9, height = 6)
```

Same for two-handed versus one-handed:

```{r, fig.width = 9, fig.height = 5}
E2 %>%
  count(HandNumber, Direction, Response) %>%
  spread(Response, n) %>%
  mutate(Sum = Monday + Friday,
         Monday = Monday / Sum,
         Friday = Friday / Sum) %>%
  select(-Sum) %>%
  gather(key = 'Response', value = 'n',
         -(HandNumber:Direction)) %>%
  mutate(Response = factor(Response,
                           levels = c('Monday', 'Friday'))) %>%
  rename(Proportion = n) %>% 
  ggplot(aes(x = Direction, y = Proportion, fill = Response)) +
  geom_bar(stat = 'identity', col = 'black',
           position = position_stack(reverse = TRUE),
           width = 0.5) + 
  scale_fill_manual(values = c('#FDE725FF', '#21908CFF')) +
  theme_minimal() +
  theme(legend.position = 'right') +
  facet_wrap(~HandNumber) +
  labs(title = 'Monday/Friday responses by\nHand Number and Gesture Direction',
       caption = str_c('N = ', nrow(E2), ', Amazon Mechanical Turk')) +
  ylab('Proportion\n') +
  xlab('\nGesture') +
  theme(plot.title = element_text(face = 'bold', size = 20, hjust = 0.5),
        axis.title = element_text(face = 'bold', size = 24),
        axis.text.x = element_text(face = 'bold', size = 20),
        axis.text.y = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 20),
        plot.caption = element_text(size = 14),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())
ggsave('../figures/experiment2_hand_number.png', width = 9, height = 6)
```

## Is there any indication of the direction effect being modulated by AQ/social skills?

Convert the scales for AQ:

```{r}
E2 <- mutate(E2,
       AQ2_face = ifelse(AQ2_face == 'strongly disagree', '1', AQ2_face),
       AQ2_face = ifelse(AQ2_face == 'slightly disagree', '2', AQ2_face),
       AQ2_face = ifelse(AQ2_face == 'slightly agree', '3', AQ2_face),
       AQ2_face = ifelse(AQ2_face == 'strongly agree', '4', AQ2_face),
       AQ2_face = as.numeric(AQ2_face),
       AQ1_face = ifelse(AQ1_face == 'strongly disagree', '1', AQ1_face),
       AQ1_face = ifelse(AQ1_face == 'slightly disagree', '2', AQ1_face),
       AQ1_face = ifelse(AQ1_face == 'slightly agree', '3', AQ1_face),
       AQ1_face = ifelse(AQ1_face == 'strongly agree', '4', AQ1_face),
       AQ1_face = as.numeric(AQ1_face))
```

Convert the scales for likeability:

```{r}
E2 <- mutate(E2,
       Likeability = ifelse(Likeability == 'strongly disagree', '1', Likeability),
       Likeability = ifelse(Likeability == 'slightly disagree', '2', Likeability),
       Likeability = ifelse(Likeability == 'slightly agree', '3', Likeability),
       Likeability = ifelse(Likeability == 'strongly agree', '4', Likeability),
       Likeability = as.numeric(Likeability),
       Warm = ifelse(Warm == 'strongly disagree', '1', Warm),
       Warm = ifelse(Warm == 'slightly disagree', '2', Warm),
       Warm = ifelse(Warm == 'slightly agree', '3', Warm),
       Warm = ifelse(Warm == 'strongly agree', '4', Warm),
       Warm = as.numeric(Warm),
       Friendly = ifelse(Friendly == 'strongly disagree', '1', Friendly),
       Friendly = ifelse(Friendly == 'slightly disagree', '2', Friendly),
       Friendly = ifelse(Friendly == 'slightly agree', '3', Friendly),
       Friendly = ifelse(Friendly == 'strongly agree', '4', Friendly),
       Friendly = as.numeric(Friendly),
       Approachability = ifelse(Approachability == 'strongly disagree', '1', Approachability),
       Approachability = ifelse(Approachability == 'slightly disagree', '2', Approachability),
       Approachability = ifelse(Approachability == 'slightly agree', '3', Approachability),
       Approachability = ifelse(Approachability == 'strongly agree', '4', Approachability),
       Approachability = as.numeric(Approachability))
```

Create sum scores:

```{r}
E2 <- mutate(E2,
             LikeScale = Friendly + Warm + Approachability + Likeability,
             AQ = AQ1_face + AQ2_face,
             LikeScale_c = LikeScale - mean(LikeScale),
             AQ_c = AQ - mean(AQ))
```

First, are these two measures correlated?

```{r}
with(E2, cor.test(LikeScale, AQ))
```

Weakly correlated.

Next, how do they correspond to the responses. For this, it'll be easiest to categorize people into high and low AQ / LikeScale based on median split ... (this is just for visualization purposes).

```{r}
# Median split for AQ:

E2$AQ_cat <- NA
E2[E2$AQ < 5 & !is.na(E2$AQ), ]$AQ_cat <- 'low'
E2[E2$AQ > 5 & !is.na(E2$AQ), ]$AQ_cat <- 'high'

# Median split for Likeability:

E2$Like_cat <- NA
E2[E2$LikeScale > 13 & !is.na(E2$LikeScale), ]$Like_cat <- 'high'
E2[E2$LikeScale < 13 & !is.na(E2$LikeScale), ]$Like_cat <- 'low'
```

Report the results:

```{r}
like_pattern <- with(E2, table(Direction, Response, Like_cat))
high <- like_pattern[, , 1]
low <- like_pattern[, , 2]
round(prop.table(high, 1), 2)
round(prop.table(low, 1), 2)
```

Visualize the main perspective-relevant result (direction) as a function of AQ:

```{r}
E2 %>%
  count(Direction, AQ_cat, Response) %>%
  filter(!is.na(AQ_cat)) %>% 
  ggplot(aes(x = Direction, y = n, fill = Response)) +
  geom_bar(stat = 'identity', col = 'black',
           position = 'dodge') + 
  scale_fill_viridis_d(option = 'D', direction = -1) +
  theme_minimal() +
  theme(legend.position = 'top') +
  facet_wrap(~AQ_cat)
```

Visualize the main perspective-relevant result (direction) as a function of likeability of the person:

```{r}
E2 %>%
  count(Direction, Like_cat, Response) %>%
  filter(!is.na(Like_cat)) %>% 
  ggplot(aes(x = Direction, y = n, fill = Response)) +
  geom_bar(stat = 'identity', col = 'black',
           position = 'dodge') + 
  scale_fill_viridis_d(option = 'D', direction = -1) +
  theme_minimal() +
  theme(legend.position = 'top') +
  facet_wrap(~Like_cat)
```

## Model this with logistic regression:

Sum-code the categorical predictors:

```{r}
contrasts(E2$Direction) <- contr.sum(2) / 2 * -1
contrasts(E2$HandShape) <- contr.sum(2) / 2 * -1
contrasts(E2$HandNumber) <- contr.sum(2) / 2 * -1
```

Set the parameters for a Bayesian analysis:

```{r}
# For parallel processing:

options(mc.cores=parallel::detectCores())

# For handling the MCMC sampling:

my_controls <- list(adapt_delta = 0.99,
                    max_treedepth = 13)
```

Set regularizing priors on betas:

```{r}
my_priors <- c(prior(normal(0, 1), class = b))
```

Specify and run the model:

```{r, message = FALSE}
E2_mdl <- brm(Response ~ Direction * HandShape * HandNumber,
              data = E2,
              family = bernoulli,
              init = 0,
              chains = 8,
              warmup = 2000,
              iter = 8000,
              prior = my_priors,
              control = my_controls,
              seed = 42)
save(E2_mdl, file = '../models/E2_mdl.RData')
```

Summarize the model:

```{r}
summary(E2_mdl)
```

Plot marginal effects:

```{r}
conditions <- make_conditions(E2_mdl, 'Direction')
marginal_effects(E2_mdl, effects = 'HandShape:HandNumber',
                 conditions = conditions)
```

Check how many of the posteriors were in the predicted direction:

```{r}
# To aid interpretation:

levels(E2$Response)
contrasts(E2$Direction)
contrasts(E2$HandShape)

# Extract posterior samples:

mypost <- posterior_samples(E2_mdl)

# Posterior probability of the language effect being above 0:

sum(mypost$b_Direction1 > 0) / nrow(mypost)

# Same for the hand shape effect:

sum(mypost$b_HandShape1 > 0) / nrow(mypost)

# Same for the hand shape effect:

sum(mypost$b_HandNumber1 > 0) / nrow(mypost)

# Check interaction with hand number:

sum(mypost$'b_Direction1:HandNumber1' > 0) / nrow(mypost)
```

## Check influence of AQ / likeability on direction:

Model with likeability/AQ * direction interaction.

```{r}
E2_social_mdl <- brm(Response ~ Direction * (AQ + LikeScale_c),
              data = E2,
              family = bernoulli,
              init = 0,
              chains = 8,
              warmup = 2000,
              iter = 8000,
              prior = my_priors,
              seed = 42,
              control = my_controls)
save(E2_social_mdl, file = '../models/E2_social_mdl.RData')
```

Check:

```{r}
summary(E2_social_mdl)
```

Values with AQ are discussed with inverted coefficients in the paper (due to how the AQ questions have been coded above).

Check the posterior values:

```{r}
mypost <- posterior_samples(E2_social_mdl)

# Direction * AQ interaction:

sum(mypost$'b_Direction1:AQ' > 0) / nrow(mypost)

# Direction * likeability interaction:

sum(mypost$'b_Direction1:LikeScale_c' > 0) / nrow(mypost)

# Probability of the likeability interaction being stronger than the AQ interaction?

sum(mypost$'b_Direction1:LikeScale_c' > mypost$'b_Direction1:AQ') / nrow(mypost)

```


Plot the LikeScale effect:

```{r, fig.width = 8, fig.height = 6}
marginal_effects(E2_social_mdl, effects = 'Direction:LikeScale_c')
```

Save the results outside for subsequent meta-analysis:

```{r}
write_csv(E2, '../data/cleaned_data/E2_cleaned.csv')
```

## Planning for other experiments

Find the hand shape for which the effect is strongest:

```{r}
# Flat hand shape:

E2_tab <- with(filter(E2, HandShape == 'flat'), table(Direction, Response))
E2_tab
chisq.test(E2_tab)$statistic
chisq.test(E2_tab)$stdres

# Push hand shape:

E2_tab <- with(filter(E2, HandShape == 'push'), table(Direction, Response))
E2_tab
chisq.test(E2_tab)$statistic
chisq.test(E2_tab)$stdres
```

Push and flat about equal.

This completes this analysis.


